### 2022-11-01 NSF2022/Description/specificaim1.tex
pushed organizational changes

\subsection{Specific Aim 1: Measuring material properties of amphiphile
  self-assembly}
\label{subsec:specific_aim_1}
Specific Aim 1 proposes a novel mathematical model for particle
self-organization driven by long-range interfacial forces. 
The research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.
Applications in this area include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-changes
\cite{McBr21, HaBr20}.

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/Domain.jpg}
 \caption{\label{fig:flow_map}
   In the HAP formulation,
   a system of exterior problems 
   defines the hydronamic and hydrophobic interactions.
   The colormap is for the intensity of $u$.
   The dynamics lead to self-organized structures like a vesicle bilayer.}
\end{wrapfigure}

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. We then use a
second-order Adams-Bashforth method to update the particle configuration.
Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional takes the form 
\begin{equation}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{equation}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

\begin{wrapfigure}[10]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/3Particles.jpg}
 \caption{\label{fig:3particles}
   \footnotesize
   Particles translate and rotate to lower the free energy $F[u]$
   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
   The arrows are the velocity field $\mathbf{u}$.
 }
\end{wrapfigure}
The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

%By solving the above system, we obtain translational and angular
%velocities of the many-body system. A second-order Adams-Bashforth
%scheme updates the particle positions and orientations.

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time-step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently.

%and
%\begin{equation}
%  \label{eq:force}
%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
%  \dif s = T_i, \qquad i=1,\ldots,N_b,
%\end{equation}
%where
%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
%particle outward normal.

@@

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}
Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[13]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, long time.
  }
\end{wrapfigure}
Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

@@

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control surface properties independently, 
which can be difficult to accomplish experimentaly 
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density function for 
relative orientation of adjacent particles
for the three boundary condition cases:
(a) is unimodal with a peak at $\theta = 0$,
(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
This kind of information can be used as an indicator
of the collective morphology. As another example,
it is costly or difficult to manufacture
Janus particles with uniform shape.
Thus, we can replace the idealistic boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function is asymptotic to a normal distribution with variance
like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example.

>>>>

\subsection{Specific Aim 1: Measuring material properties of amphiphile
  self-assembly}
\label{subsec:specific_aim_1}
%The goal of this collaborative proposal is to use mathematical modeling
%and numerical simulations to investigate the dynamic self-assembly of
%amphiphilic particles interacting via hydrophobic forces in solvent.
This collaborative proposal aims to advance
the mathematical modeling and numerical simulation
of dynamic self-assembly of amphiphilic particles interacting
via hydrophobic forces in solvent.
Amphiphilic particles such as lipid molecules possess both hydrophobic
and hydrophilic structures. In a viscous solvent they self-assemble into
meso-/macroscopic structures such as micelles and bilayers of lipids to
shield their hydrophobic surfaces from contact with the solvent
molecules e.g., waters. Such self-assembly of amphiphiles via hydrophobic
forces is ubiquitous in biology~\cite{Israelachvili1954},
and has been a major source of nonspecific interactions 
in soft matter~\cite{Sanchez-IglesiasEtAl2012_ACSNano,
AltantzisEtAl2013_PSC, XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the
%self-assembly dynamics of amphiphilic particles so to design smart
%materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.

%The hydrophobic force arises when polar solvent molecules come in
%contact with a non-polar substance, such as hydrocarbon or vapor.
%In a polar solvent (like water), the dipole-dipole interaction between
%solvent molecules form a loosely structured hydrogen-bond network where
%each solvent molecule shares bonds with neighboring molecules at any
%given time \cite{Israelachvili1954}. In the presence of a non-polar
%solvent molecule loses the ability to form hydrogen bonds
%in one direction. 
%The decrease in the number of hydrogen bonds causes a reorientation,
%or structural change, in the surrounding water that is energetically
%very unfavorable \cite{Bjorneholm2016}.

\begin{wrapfigure}[15]{r}{0.37\textwidth}
\vspace{-8pt}
\centerline
{
\includegraphics[width=0.36\textwidth]{figures/Background/LongRangeForce.jpg}
}
%\vspace{-20pt}
\caption{\label{fig:force_distance}
Force-distance curve for surfactant
monolayers adsorbed on mica reveals a long-range
attraction~\cite{Lin2005}.}
\end{wrapfigure}

Macroscopically, the substantial free energy of placing hydrophobic
surfaces in contact with water is roughly proportional to the surface
area of the contact region~\cite{Bjorneholm2016}.
%As a result, hydrocarbon solutes have a large interfacial tension 
%and try to minimize their surface area when in water. 
At the microscopic level, however, there is long-range interaction
between hydrophobic surfaces. Two hydrophobic surfaces, in particular,
separated by water over some distance, experience an attraction
called the
hydrophobic force~\cite{Lum1999, Meyer2006, Hammer2010, KaScScNe16}.
The force is nonadditive~\cite{SilveraBatista1242477},
and measurements show that the hydrophobic force decays exponentially with a
decay length on the order of 1--10 nm~
\cite{Israelachvili1984,Marcelja1977,Christenson2001,Lin2005,Taetal13}
(Figure \ref{fig:force_distance}).

Motivated by its broad applicability to biology, chemistry, and engineering,
PIs RR and YNY developed a mathematical model, called the
hydrophobic attraction potential (HAP) model~\cite{Fu2018_SIAM},
that is based on
the linear response of water to surface perturbations. This model was
used by all the PIs to show how amphiphilic Janus particles (JP)
self-assemble into a vesicle-like structure~\cite{FuQuRyYo20}.
Janus particles are typically spherical particles with a biphasic
material label on either hemisphere \cite{CaFaRaVe89,Gaetal13,Mallory2017,HaBr20,McBr21}.
Based on
preliminary results (\S\ref{sec:preliminary_work}), the PIs propose to
extend this HAP model as a general methodology that leads
to new mathematical ideas and efficient numerical methods.

\subsection{Hydrophobic attraction}
The hydrophobic attraction potential theory concerns the self-organization of
hydrophobic particles in a viscous solvent. It is a phenomenological
model mimicking the linear-response of water to surface perturbations
and stems from work of Stjepan Mar\v{c}elja
from the Australian National University in 1976. To explain certain
repulsion measurements between lecithin bilayers, Mar\v{c}elja and
coworkers devised a mathematical model using a Landau expansion of the
free energy density of an order parameter for the orientation of
water~\cite{LeRaPa77, MaRa76, LANDAULIFSHITZ5}. Their truncated free
energy gave a boundary value problem for water structure that was
readily solved in terms of hyperbolic trigonometric functions.

Although schematic, the model was general enough to explain a number of
physical effects. For example, the repulsion of lecithin bilayers
was explained by the free energy that decreases with distance of
separation because of the mean orientations of water being opposite at
the two interfaces. Later, a long-range attractive force between
hydrocarbon coated mica sheets was measured up to
100~nm~\cite{ClCh88,RaDe88}. The Mar\v{c}elja
theory was then applied to this problem for an order parameter
representing the excess number of hydrogen bonds per water
molecule and gave agreement with the measured force
curves~\cite{ErLjCl89}.

%\begin{wrapfigure}[7]{r}{0.32\textwidth}
%  \vspace{-0pt}
%  \centering
%  \includegraphics[width=0.32\textwidth]{figures/Background/ChandlerWeeks.pdf}
%%  \vspace{-20pt}
%  \caption{\label{fig:chandler_weeks}
%  }
%\end{wrapfigure}
%\todo{This figure is not referenced in the text.}
Analogues of Mar\v{c}elja's phenomenological theory appeared in other
areas related to biological self-assembly, such as interactions of
membrane-bound proteins~\cite{KoNa15, Nagle17, KUZMIN2005} and the 
theory of polymer bead interaction in mixed
solvents~\cite{deGe76}.
%In the latter, the free energy corresponds to
%the Ornstein-Zernike form of the order parameter correlation function.
On the downside, it applies a continuum theory to distances of a few
molecular diameters, the association of order parameter is arbitrary, it
predicts monotonic forces, and finally the theory does not account
for the amplification in attraction at very short distances~\cite{Ni80}.

\begin{wrapfigure}[21]{l}{0.3\textwidth}
  \vspace{-5pt}
\includegraphics[width=0.3\textwidth]{figures/Background/Fissure.jpg}
\includegraphics[width=0.3\textwidth]{figures/Background/Landscape.jpg}
\caption{\label{fig:fissure} In fusion, fissures in the phospholipid
  monolayers expose hydrocarbon to water (top). The energy of fissures
  dominates first and third stages of fusion (bottom).
}
\end{wrapfigure}
Despite the ubiquity of
the phenomenon, theoretical developments explaining the basic underlying
principles of the hydrophobic effect have come relatively
late~\cite{Ch05}.
No single theory has been able to account, either qualitatively
or quantitatively,
for hydrophobic interaction over the full distance
regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
For example, studies of the partitioning of
hydrophobic solutes provide estimates for the energy cost of creating
hydrophobic-water contacts
that is a factor of three lower than the value derived from interfacial
tension measurements. Only recently was an explanation for this
discrepancy provided~\cite{Jackson2016}.

The continuum approach to water structure
that we present here is justified
\textit{a posteriori} by the agreement between theory and experiment.
Researchers have used Mar\v{c}elja's theory to calculate
energies of pore formation and fusion~\cite{Gletal88, Aketal17,
RyKlYaCo16}.
%When open, the attraction between apposing hydrophobic
%surfaces causes the fissure to collapse.
PI RR calculated a least energy path 
of fusion using a modified form of the Helfrich energy that
included Mar\v{c}elja's free energy for the structure of water
separating fissures~\cite{RyKlYaCo16} (Figure~\ref{fig:fissure}).
The calculated barrier heights were 
corroborated experimentally \cite{FrRoPi17}. In summary,
there is a consensus that despite its apparent simplicity, the predictions
of the hydrophobic attraction potential theory are compatible with
experimental measurements and may closely mirror the reality of
the physical process at a molecular scale~\cite{FrRoPi17, Fretal21}.

The HAP is a conceptual advance for modeling bilayer membranes.
Continuum elastic energies of membrane assume an energy density that
depends quadratically on the bilayer strain
\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The coefficients
of the continuum ansatz correspond to experimentally measured elastic
moduli \cite{Nagle17, Nagle17-2, NAGLE2000159}.  The HAP approach can
potentially explain membrane properties from first principles because it
derives elastic energies assuming parameters for the water structure and
particle shape \cite{Fu2018_SIAM, FuQuRyYo20, doi:10.1063/5.0009734,
LiAn-Chang16}.  Immersed boundary and boundary integral are highly
effective for modeling intact, giant unilamellar vesicles (GUV) because
they use relatively large time-step sizes and mesh sizes
\cite{
Shravan09,
Rahimian15,
KimLai2010_JCP,
KimLai2012_PRE,
HuLaiSeolEtAl2016_JCP,
Bartels,
Peng13,
RyKlYaCo16,
Sinha15,
Lowengrub13,
Hu,
Hu13}.
Conversely, the number of coarse-grained particles needed to track a GUV
in the HAP formalism is relatively large.  For microscopic process like
fusion, however, membrane deformations occur at a length scale
comparable to the thickness of the membrane
\cite{Kuzmin7235,Aeffner2012,KoKo2002}.  The small deformation
assumption of continuum theory no longer holds
\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The HAP theory
does encode membrane thickness through particle diameter, and it is
comparatively straightforward to account for proteins and lipid mixtures
by including several particle species.  Any ruptures or insertions occur
self-consistently in the HAP formulation.  Phase-field and level-set
methods also allow for topological changes but they require multiple
phase fields and level sets and additional (sometimes empirical) laws to
couple them to model membrane-membrane interactions
\cite{
DuLiuWang2004_JCP,
BibenKassnerMisbah2005_PRE,
DoyeuxGuyotChabannesEtAl2013_JCAM,
Du05,
QiangDu08,
doi:10.1098/rspa.2012.0505,
doi:10.1137/130941432,
Feetzl18,
doi:10.1137/16M1108406}.
In addition, these methods require the entire fluid and interfacial
domains to be discretized.  In contrast, the HAP methodology allows
evolution equations to be solved using integral equation methods that
when optimized have linear or near-linear computational complexity in
the number of particles~\cite{fmm1, fmm2, fmm3, fmm4, fmm5, fmm6, fmm7,
fmm8}.

Specific Aim 1 proposes a novel mathematical model for particle
self-organization driven by long-range interfacial forces. 
The research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.
Applications in this area include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-changes
\cite{McBr21, HaBr20}.

@@

\begin{wrapfigure}[9]{r}{0.65\textwidth}
  \vspace{-20pt}
  \begin{center}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  positive/negative charge (right). The dashed curve is the boundary of the
  disk and the arrow is its director for each particle.}
\end{wrapfigure}
Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[13]{l}{2in}
  \vspace{-4pt}
  \centering
  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:OrderPDFs}
    Probability density functions for
    relative orientation of nearby particles
    for the data in 
    Figure~\ref{fig:self-assembly}, long time.
  }
\end{wrapfigure}
Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity that is greater
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

@@

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

The ultimate goal is to use numerical simulations to aid
the syntheses of soft matter materials.
Here, mathematical models like the kind we propose are crucial
because the model parameters control surface properties independently, 
which can be difficult to accomplish experimentaly 
~\cite{Bradley2016,Mallory2017,Bradley2017}.
The ability to translate phenomenological parameters
into measurable quantities is important. 
For example, Figure~\ref{fig:OrderPDFs} plots
the probability density function for 
relative orientation of adjacent particles
for the three boundary condition cases:
(a) is unimodal with a peak at $\theta = 0$,
(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
This kind of information can be used as an indicator
of the collective morphology. As another example,
it is costly or difficult to manufacture
Janus particles with uniform shape.
Thus, we can replace the idealistic boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function is asymptotic to a normal distribution with variance
like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example.
%\hl{Collaboration with experimental groups will
%use numerical methods to predict parameter regimes 
%to control particle-particle interactions.}

%\begin{wrapfigure}[14]{l}{0.5\textwidth}
%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
%\caption{\label{fig:multilamelar}
%  Experimentalists can transform unilamellar vesicles to% multilamellar
%  vesicles by altering the quality of the solvent
%    \cite{deMeetal21}.
%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
%  $f(u)$ and boundary conditions. 
%}
%\end{wrapfigure}
